Spá: a web-based viewer for text mining in Evidence Based Medicine

### 2014-04-24 documentation/paper.tex
some updates on the paper

Summarizing the evidence about medical interventions is an immense undertaking.
Unstructured PDF documents remain the main vehicle for disseminating the results of clinical trials.
Expert clinicians and researchers typically manually extract and synthesise information about effectiveness, adverse effects, and trial quality, which are published as \emph{systematic reviews}.
We introduce Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}}, a web-based PDF viewer which uses machine learning modules to semi-automate the task of PDF annotation and summarisation.
As an example, we demonstrate the use of Spá to semi-automate the assessment of bias in clinical trials.
Spá allows the use of hybrid models which simultaneously classify PDF documents (specifically identifying trials at low risk of various biases), and also annotate sentences or words which contribute most to the classification.
Spá is modular, and new models may be trivially added, thus allowing its use in other domains with a PDF-based literature, including law, physics, and biology.

>>>>

Summarizing the evidence about medical interventions is an immense undertaking.
In part this is because unstructured PDF documents remain the main vehicle for disseminating the results of clinical trials.
Clinicians and researchers typically manually extract and synthesise information regarding effectiveness, adverse effects, and trial quality, which are then published as \emph{systematic reviews}.
We introduce Spá\footnote{Source code available under GPLv3 at \url{https://github.com/joelkuiper/spa} \cite{kuiper2014}; demo available at \url{http://clinici.co/}}, a web-based PDF viewer that allows for annotation and summarisation machine learning modules to semi-automate the task of PDF annotation and summarisation.
To illustrate, we demonstrate the use of Spá to semi-automate the assessment of bias in clinical trials.
Spá can visualize the output from hybrid models that simultaneously classify PDF documents (e.g., identifying trials as low risk of various biases), and also annotates sentences or words that contribute most to the classification.
The Spá architecture is modular, and new models may be trivially added, thus the tool made be widely useful in other domains with a PDF-based literature, including law, physics, and biology.
